Sequential Composition for Relaxed Memory: Pomsets with Predicate Transformers

### 2021-08-09 paper/mca1.tex
adjusting address calculation to handle aliasing and TC12

Lemmas \ref{lem:monoid} and \ref{lem:if} mostly hold for \PwTmca{1}.  The
exceptions are items \eqref{lem:ifelse:if:if1} and \eqref{lem:ifelse:if:if2},
which become inclusions.  For example, \eqref{lem:ifelse:if:if1} becomes:
\begin{displaymath} 
  \xIFTHEN{\aForm}{\aPSS_1}{\aPSS_2}
  \supseteq
  \xSEMI{
    \xIFTHEN{\aForm}{\aPSS_1}{}
  }{
    \xIFTHEN{\lnot\aForm}{\aPSS_2}{}
  }
\end{displaymath}
The culprit is $\rdelay$, which introduces order regardless of whether
preconditions are disjoint.  As an example, 
\begin{math}
  \sem{\IF{r}
  \THEN \PW{x}{1}
  \ELSE \PW{x}{2}
  \FI}
\end{math}
has an execution with
\begin{math}
  (r{=}0\mid\DW{x}{2})
  \xwki
  (r{\neq}0\mid\DW{x}{1}),
\end{math}
(using augmentation), whereas
\begin{math}
  \sem{
    \IF{r} \THEN \PW{x}{1}\FI
    \SEMI
    \IF{\BANG r} \THEN \PW{x}{2}\FI
  \FI}
\end{math}
has no such execution.

For further discussion, see \textsection\ref{sec:delay}.

>>>>

Lemmas \ref{lem:monoid} and \ref{lem:if} hold for \PwTmca{1}.  For further
discussion of items \eqref{lem:ifelse:if:if1} and \eqref{lem:ifelse:if:if2},
see \textsection\ref{sec:delay}.
